### 2022-02-24 draft2.tex
draft of sections 1 and 2 including images

\begin{equation}
  F_X(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
\end{equation}
where $x_n$ is the largest value of X less than or equal to $x$.
The quantile function is defined as
\begin{equation}
  Q(p) = \inf \{ y \in \mathbb{R} : p \leq F_X(x) \}
\end{equation}
returning a quantile value where $p$ is a given probability $0\leq p \leq 1$.

@@

\begin{equation}
  p^E(x) = \sum_{jm=1}^M w_mp_m(x)
\end{equation}
where $p_m$ is the $j^{th}$ component forecast distribution and 
$0 \leq w_m \leq 1$ is a weight assigned to each component where $\sum w_m = 1$.
Methods for estimating weights include Maximum Likelihood estimation
\cite{raftery2005using}, MCMC 
sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
EM can get difficult as parameters i.e. number of distributions increase, and 
shows MCMC may be better with that high dimensionality and gives full posterior
of weights)
and minimizing the CRPS as in 
\cite{baran2018combining}.

@@

In the last few decades, increased computing power and improvements in MCMC
sampling have greatly contributed to growth in the use of
predictive distributions \cite{gneiting2007strictly}. (See examples listed in
\cite{krueger2016probabilistic}).

@@

\begin{equation}
\label{eq:kd}
  \hat{p}_n(x) = \frac{1}{n h_n} \sum_{i=1}^n K \left( \frac{x-X_i}{h_n} \right) 
\end{equation}
where $K$ is a kernel function, and $h_n$ is a bandwidth

@@

\subsection{Discretized probability bins}
A discretized bin probability distribution may be constructed over a set 
$A = [a, b]$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
to be forecasted, a forecast hub will determine the possible values for $A$ and 
select the number of bins and the sizes for each. It may the case
that a forecast hub will set the width of all bins to be equal so that 
$\Delta = b_i - b_{i-1}$ is the width for all $i$ see for example
\cite{mcgowan2019collaborative}. 
For this paper, we will consider the case where all bins share a common width.
To complete the construction, a probability $p_i$ is assigned to each $b_i$ 
where $\sum_{i=1}^{K}p_i = 1$. These probabilities are determined by the 
forecasters. 
This discrete representation with a given bin and assigned probability is in
essence a probability mass function, so a given forecast may be evaluated and 
scored the same as a discrete parametric distribution.

If the value to be forecasted takes on discrete values, a common discrete 
distribution, such as a binary or Poisson distribution, may sometimes be used to 
assign probabilities to each of the bins. When the values to be forecasted are
continuous, a forecaster may need to employ some method of discretization to a 
forecast distribution. There are a number of possible ways to do this including
those outlined by Chakraborty and Subrata \cite{chakraborty2015generating}.
In a retroactive analysis of forecast predictions from the CDC influenza 
competition, we attempt to evaluate whether some or any teams made their 
predictions by discretizing from a common continuous distribution function.

The CDC has used a discretized distribution representation as the representation
for their annual influenza forecasting competition and other disease outbreaks.
In that context it has become the standard representation 
\cite{brooks2020comparing}.

Most statistical models such as parametric models 
or distributions made from samples may be readily translated into a discretized 
distribution -see \cite{chakraborty2015generating} for a summary of several-
giving forecasters flexibility in how they build their 
models and assign probabilities. 
There is however some sacrifice in what can be 
forecasted as the possible range of the distribution may be limited to what the
forecast hub requires. This limitation is in part what prompted the COVID-19
Forecast Hub to use quantile forecasts rather than binned distributions.
\cite{bracher2021evaluating}.
In a simulation study outlined later, we will
consider a construction from Kemp \cite{kemp2004classes} to discretize known
continuous distributions.

\subsection{Quantile representation}
Uncertainty in a forecast prediction may also be characterized by  including
multiple quantiles along with corresponding values. Often the median value will
be reported as a point forecast with a number of quantiles included which form 
confidence intervals of various levels.
A quantile forecast is constructed as follows.
For $N$ given quantiles $\alpha_1,..., \alpha_N$, $q_1,..., q_N$ are the values
such that

\begin{equation}
  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., 
  P(Y \leq q_N) = \alpha_N
\end{equation}

When the quantiles are reported as a median and confidence intervals we have

\begin{equation}
  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., P(Y \leq q_k) = .5, 
  ..., 
  P(Y \leq q_{N-1}) = 1 - \alpha_{N-1}, P(Y \leq q_N) = 1 - \alpha_N
\end{equation}

The COVID-19 Forecast Hub requires that participating teams report their
forecasts as quantile values corresponding to 23 or 7 quantiles -depending on 
the target or time being forecasted. The quantile representation was selected
over the discretized bins used in the influenza competition because the range 
of observation outcomes of interest was much larger and an appropriate binning
scheme would have been difficult to define \cite{bracher2021evaluating}.

The quantile or interval format is somewhat unique among forecast 
representations discussed in this paper. What is possible for scoring forecasts
or building ensemble models in other representations is often not possible with
quantile forecasts. Yet it has its advantages.

Quantile representation allows for forecasters to submit fairly detailed
forecasts without restricting the range of possible values -a major reason for 
selecting a quantile representation over discretized bins 
\cite{bracher2021evaluating}.

Since quantiles are easily calculated from any regular distribution type
-e.g. inverse CDF for parametric functions and inverse ECDF from data or 
samples- we consider quantile forecasts to have high flexbility in terms of 
shape and range.

As in the
discretized representation, the resolution of a distribution based on quantiles
will depend on the number of quantiles to be forecasted. There is however a 
significant loss of information in reporting the extreme outcomes in a quantile
model. Since reported intervals can only be so wide, it is possible that tail 
information is lost. The COVID-19 Forecast Hub for example requires forecast 
values up to the $99^{th}$ and down to the $1^{st}$ percentile. For values any
more extreme, exactly assigning probabilities is impossible.

\subsection{Discrete mixture of parametric distributions}
In a parametric setting, forecasters may be permitted to submit a forecast as a
discrete mixture. Such a distribution may be constructed in the same way as the
ensemble described under Parametric distributions where for $T$ models with pdf
$p_t(y|\theta)$ $p^{M} = \sum_{t=1}^T z_tp_t(y|\theta)$ where 
$z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$

Like the standard parametric model, a discrete mixture is easily evaluated with
exisiting software (like distr R package) (cite??) and scoring may be done by 
most or all of the same methods. The resolution of a discrete mixture is high 
and the support need not be limited by submission requirements.

An ensemble model may be built by constructing a mixture of mixtures. Where for 
$J$ forecasts $p^{E}(y|\theta) = \sum_{j=1}^{J} w_j p^{M}_j(y|\theta)$ where 
$w_j > 0$ and $\sum_{j=1}^J w_j = 1$. (is it necessary to describe this
construction).

Depending on the number of components a forecaster includes in a mixture 
forecast, the amount of storage per forecast might be as little as for a 
parametric forecast and as much as a forecast hub will allow.

@@

\section{Forecast specifics on scoring, ensembling, etc.}

\subsection{Scoring}

Because the probability evaluation is only at the observed 
point \cite{reich2019accuracy} used a modified Logarithmic score 
known as the multibin logarithmic score (MBlogS) for scoring
forecasts. This allowed for a range of values to be considered "correct" or 
accurate. MGlogS is defined as

\begin{equation}
  MBlogS(F_m, y^*) = log(\sum_{i=-d}^{d} p_m(y^* + i))
\end{equation}

\begin{equation}
  \int_{y*-\epsilon}^{y^*+\epsilon} -log\;p_m(y^*) (??)
\end{equation}

The MBlogS has the advantage of offering a more accesible interpretation but the
drawback of being improper \cite{bracher2021evaluating}.

Another commonly used score, the interval score, may also be used on density 
forecasts including discretized bin forecasts. With the right smoothing of
a distribution of drawn samples, 
such as Gaussian approximation or Kernel density estimation, these methods may 
be used for scoring, see for example \cite{krueger2016probabilistic}.
These scoring methods will not work for raw samples however.

The Continuous ranked probability score (CRPS) is a function of a CDF $F$, 
including an Empirical CDF, $\hat{F}(x) = n^{-1} \sum_{i=1}^n 1\{x \geq X_i\}$
and so 
can be used a bit more extensively. For the CDF $F_m$, the CRPS is defined as

\begin{equation}
  CRPS(F_m, y^*) = \int_{-\infty}^{\infty} (F_m(y) - 1_{\{y*\leq y\}})^2 dy
\end{equation}

For a forecast of drawn samples, the ECDF may be computed and the CRPS used to 
score the prediction.

The Interval score (IS), a consistent and elicitable proper score 
(see \cite{gneiting2014probabilistic} for definitions) is defined as

\begin{equation}
  IS_{\alpha}(l,r; y^*) = (r-l) + \frac{2}{\alpha}(l-y^*)1\{y^*<l\} 
  + \frac{2}{\alpha}(y-r)1\{y>r\}
\end{equation}

where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
the central $(1-\alpha)$ prediction interval. This is a sum -weighted by 
$\alpha$- of the width of the
interval and the distance between $y^*$ and the interval (if $y^*$ is not 
captured in the interval). The IS requires only a single central 
$(1-\alpha) \times 100$ prediction interval.

When an interval forecast is made up of more than one interval with different
$\alpha$ levels, a weighted interval score (WIS) may be evaluated. Bracher et.
al use the WIS to evaluate COVID-19 inverval forecasts 
\cite{bracher2021evaluating}. There are multiple versions of the WIS -some of 
which are described by Bracher et. al- but that used in the COVID-19 Forecast
Hub is defined as follows.

\begin{equation}
  WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,y) \} )
\end{equation}

where $F_m$ is the interval forecast, $K$ is the number of prediction intervals
each with level $\alpha_k$ and $med$ is the predictive median. $\alpha_0 = 1$ is 
is the $\alpha$ value corresponding to the predictive median which may also be
considered a level 0 prediction interval. $w_k = \alpha_k/2$ is the weight on
intervals which was used. With that choice of weights, it may be shown that the
WIS approximates CRPS see S1 Text  \cite{bracher2021evaluating} or

\begin{equation}
  WIS_{0,K}(F_m,y^*) \approx CRPS(F_m,y^*)
\end{equation}

\subsection{Flexibility, resolution and information (such as tail info)}
The amount of info

\subsection{Ensemble}

Reich et. al used BMA to combine multiple forecasts from the flu 
competition. There built and compared ensemble models with different weighting
schemes including equally weighted components $w_j = 1/J$ and estimating weights
according to the model specification. To estimate weights they used the 
Expectation Maximization (EM) algorithm \cite{reich2019accuracy}. See the
supplementary material for details. Other options for estimating the weights 
include Monte Carlo Markov Chain sampling ??\cite{vrugt2008ensemble} or a 
minimization of the ensemble CRPS score \cite{baran2018combining}.

The BMA ensemble construction works for discrete and continuous parametric 
distributions as well as discretized bin distributions, but is not useful when 
the forecasts are of the interval type.

Quantile averaging or Vincentization is defined as

\begin{equation}
  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
\end{equation}

where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
$0 < \alpha \leq 1$. Some notable characteristics are that it is more likely
to be unimodal than linear averaging of densities like BMA 
\cite{busetti2017quantile} (this paper is a big comparison of QMA and 
linear or log averaging. Under some circumstances, such as when member
distributions are exponential, Weibull or logisitic the aggregated distribution
is the same \cite{ratcliff1979group}. It apparently produces smoother
distributions than BMA, at least in \cite{schepen2015model}.

These dudes seem to think averaging quantiles is better than simple averaging 
probabilities. More sharp (less variation), perform better in scoring etc.
\cite{lichtendahl2013better}.

\subsection{Storage}

The data requirement for a parametric distribution small and will usually be the 
least when compared with other representations. As long as the forecast is 
allowed to have an unbounded range, only 3 or 4 pieces of information will be
required including specification of the distribution family and model 
parameters. See the table below for an example of a normal distribution with 
mean 0 and variance 1.

With those three pieces of information, the whole distribution is completely
defined and software is readily available for calculating moments, percentiles,
probabilities and generating random samples. The third box under param3 is there
in case a particular distribution family has three parameters -a location-scale
T distribution for example.

If the distribution is made up of samples from a distribution, like posterior
predictive distribution, much more space will be required to contain all the 
information. A sample using MCMC sampling may have thousands or even tens of 
thousands of draws. It's easy to see why this could be a problem if millions of
predictive distributions are collected and saved.

The exact amount of information required for a discretized bin forecast will 
vary depending on permitted range of the forecast and the desired resolution. 
In the CDC flu contest, a forecast could have 131 bins between 0\% and 13\% 
-bins having increments of 0.1- with 
corresponding probabilities in each. That makes 262 pieces of information per
prediction. A much larger number than what is required for a fully defined
parametric distribution. The following table shows what a discretized standard
normal distribution looks like in 131 discretized bins. Note that for the sum of 
the probabilities to equal one, it was essential to normalize the probabilites
within the range $[-6.5,6.5]$ since the full range of a normal distribution is
$(-\infty, \infty)$.

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|} 
 \hline
    bin & prob \\ \hline
    ... & ... \\
    {[1.4,\;1.6)} & 0.04414 \\
    {[1.6,\;1.8)} & 0.05896 \\
    {[1.8,\;2.0)} & 0.07032 \\
    {[2.0,\;2.2)} & 0.07172 \\
    {[2.2,\;2.4)} & 0.07955 \\
    ... & ... \\
 \hline
 \end{tabular}
\end{table}

Like in the last two representations, data storage for interval forecasts will
depend on the desired clarity of resolution. For the COVID-19 forecasts 
submitted to the forecast hub, twenty-three quantile values are requested for 
the quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This included a 
median along with eleven confidence intervals \cite{bracher2021evaluating}. This
requires forecasters to submit forty-six values in each short-term forecast 
(some of the longer term forecasts only include seven quantiles). In terms of 
storage, this is an improvement over requirements for the flu contest.

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|} 
 \hline
    quantile & value \\ \hline
    0.01 & 1.07137 \\
    0.025 & 1.2404 \\
    0.05 & 1.40689 \\
    0.01 & 1.62675 \\
    ...  & ... \\
    0.9 & 4.50667 \\
    0.95 & 5.18328 \\
    0.975 & 5.82391 \\
    0.99 & 6.58783 \\
 \hline
 \end{tabular}
\end{table}

>>>>

\begin{equation}
\label{eq:dcdf}
  F_X(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
\end{equation}
where $x_n$ is the largest value of X less than or equal to $x$.
The quantile function is defined as
\begin{equation}
  Q(p) = \inf \{ y \in \mathbb{R} : p \leq F_X(x) \}
\end{equation}
returning a quantile value where $p$ is a given probability $0\leq p \leq 1$.

@@

\begin{equation}
\label{eq:bma}
  p^E(x) = \sum_{jm=1}^M w_mp_m(x)
\end{equation}
where $p_m$ is the $j^{th}$ component forecast distribution and 
$0 \leq w_m \leq 1$ is a weight assigned to each component where $\sum w_m = 1$.
Methods for estimating weights include Maximum Likelihood estimation
\cite{raftery2005using}, MCMC 
sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
EM can get difficult as parameters i.e. number of distributions increase, and 
shows MCMC may be better with that high dimensionality and gives full posterior
of weights)
and minimizing the CRPS as in 
\cite{baran2018combining}.

@@

So the options that a researcher has for constructing a forecast are more than
if they are asked to submit a parametric distribution and the characterisitcs 
and potential shapes of distributions is much larger.
In the last few decades, increased computing power and improvements in MCMC
sampling have greatly contributed to growth in the use of
predictive distributions \cite{gneiting2007strictly}. (See examples listed in
\cite{krueger2016probabilistic}).

@@

\begin{equation}
\label{eq:kd}
  \hat{p}_n(x) = \frac{1}{n h_n} \sum_{i=1}^n K \left( \frac{x-X_i}{h_n} \right) 
\end{equation}
where $K$ is a kernel function, and $h_n$ is a suitable bandwidth. GA is defined
as

\begin{equation}
\label{eq:ga}
  \hat{F}_n(x) = \Phi  \left( \frac{x-\hat{\mu}_n}{\hat{\sigma}_n} \right)
\end{equation}
where $\Phi$ is the standard normal CDF and $\hat{\mu}_n$ and $\hat{\sigma}_n$
are the empirical mean and standard deviation of the sample $(X_i)$. (See
\cite{krueger2016probabilistic} for definitions of \ref{eq:kd} and \ref{eq:ga}).

@@

To build an ensemble model from sample distribution forecasts, the BMA 
construction from (\ref{eq:bma}) would work only replacing $p_m$ with 
$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$. Here as well the optimal weights 
$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. Then 
the ensemble distribution would take the form of a continuous or discrete
probability mixture distribution. If the desire is that the ensemble still be
a sample distribution, after selecting weights, a sample may be selected by 
randomly selecting a sample from $(X_n)_m$ with probability $w_m$.

A potentially big issue with using sample distributions is the amount of storage
it would require. For example when making MCMC draws from a posterior 
distribution, the final sample distribution can have a sample size of thousands
or tens of thousands. Maybe not all distributions would require such a large 
sample size, but sizes of at least dozens or hundreds would be required for each
forecast prediction. For any project the size of the CDC flu competition or the
COVID-19 Forecast Hub, the storage required would be large and potentially 
expensive.

\subsection{Discretized bin distributions}
An alternative to parametric distributions and sample distributions which allows
for high flexibility in distribution shape but is more manageable in terms of 
storage is a discretized bin distribution.

A discretized bin probability distribution may be constructed over a set 
$A = [a, b]$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
to be forecasted, a forecast hub will determine the possible values for $A$ and 
select the number of bins and the sizes for each. It may be the case
that a forecast hub will set the width of all bins to be equal so that 
$\Delta = b_i - b_{i-1}$ is the width for all $i$ see for example
\cite{mcgowan2019collaborative}.
To complete the construction, a probability $p_i$ is assigned to each $b_i$ 
where $\sum_{i=1}^{K}p_i = 1$. These probabilities are determined by the 
forecasters. 
This discrete representation with a given bin and assigned probability is in
essence a probability mass function in that the calculation of moments and the 
the cumulative distribution are done the same as for a discrete parametric 
distribution. For a random variable X from a binned distribution to calculate
the $j^{th}$ moment we may use

\begin{equation}
\label{eq:bev}
  EX^j = \sum_{i=1}^n \beta_i^j p_i
\end{equation}
where $\beta_i$ is a value related to the bin $B_i$ such as $\beta_i = b_i$,
$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$. The 
cumulative distribution may be

\begin{equation}
\label{eq:bcdf}
  P(X \leq b) = \sum_{i=1}^n p_i
\end{equation}
where $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.

If the value to be forecasted takes on discrete values, a common discrete 
distribution, such as a binary or Poisson distribution, may sometimes be used to 
assign probabilities to each of the bins. When the values to be forecasted are
continuous, a forecaster may need to employ a method of discretization to a 
forecast distribution. There are a number of possible ways to do this including
those outlined by Chakraborty and Subrata \cite{chakraborty2015generating}.

The CDC has used a discretized distribution representation as the representation
for their annual influenza forecasting competition and other disease outbreaks.
In that context it has become the standard representation 
\cite{brooks2020comparing}. A decent amount of work has been done in evaluating 
and constructing ensemble models on influenza forecasts represented by 
discretized bins \cite{mcgowan2019collaborative}, \cite{mcandrew2019adaptively}
\cite{reich2019collaborative}.

Because discretized bins can be seen as a pmf, methods for proper scoring 
already 
discussed -LogS and CRPS- are useable and BMA is valid method for ensemble 
construction. Reich et. al used BMA to combine multiple forecasts from the flu 
competition. There built and compared ensemble models with different weighting
schemes including equally weighted components $w_j = 1/J$ and estimating weights
according to the model specification. To estimate weights they used the 
Expectation Maximization (EM) algorithm \cite{reich2019accuracy}. See the
supplementary material for details.

The exact amount of information required for a discretized bin forecast will 
vary depending on permitted range of the forecast and the desired resolution. 
In the CDC flu contest, a forecast could have 131 bins between 0\% and 13\% 
-bins having increments of 0.1- with 
corresponding probabilities in each. That makes 262 pieces of information per
prediction. For any binning scheme of more than two bins, the information 
requirement for discretized bins will be higher than for parametric distrbutions.
Table \ref{tab:dbins} illustrates what a discretized 
Lognormal$(1,0.4)$ distribution truncated over $[0,8]$
looks like in 41 equally spaced discretized bins. The discretization was done
such that

\begin{equation}
\label{eq:disc}
  p_i = \int_{b_{i-1}}^{b_i} p^{TL}(x) dx
\end{equation}
where $p^{TL}$ is the pdf of a truncated Lognormal$(1,0.4)$. This is similar
to Methodology-IV from Chakraborty \cite{chakraborty2015generating}
 \cite{kemp2004classes}.

\begin{table}[h!]
\centering
\label{tab:dbins}
 \begin{tabular}{|c|c|} 
 \hline
    bin & prob \\ \hline
    ... & ... \\
    {[1.4,\;1.6)} & 0.04414 \\
    {[1.6,\;1.8)} & 0.05896 \\
    {[1.8,\;2.0)} & 0.07032 \\
    {[2.0,\;2.2)} & 0.07172 \\
    {[2.2,\;2.4)} & 0.07955 \\
    ... & ... \\
 \hline
 \end{tabular}
\end{table}
Submitted as a forecast prediction, the distribution in table \ref{tab:dbins} 
includes 82 pieces of data. For parts 
of the CDC influenza competition some forecasts included upt to 262. This is 
much more manageable than possible thousands of samples from a samle 
distribution but is 
still much larger than the 3 or 5 data pieces required to report a lognormal
or truncated lognormal distribution.

Depending on what is known about the problem to be solved, creating the right 
binning scheme might be a challenge. Because there must be a finite number of
bins, forecast distributions must have a finite support. Where the range of 
possible outcomes to a problem is little known, the right binning scheme may be
hard to produce.

\subsection{Quantile representation}
When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
the time pressure of generating forecasts and the consideration of the large
range for possible outcomes contributed to the COVID-19 Forecast Hub decision
to forego trying to create the right binning scheme and use sets of prediction
intervals to represent uncertainty in predictions \cite{bracher2021evaluating}.

The Forecast Hub requires predictions to be submitted as 11 or 3 nominal 
intervals -depending on the specific target- and a median.
Using this interval or quantile representation lead to a number of changes in 
the evaluation and aggregation of forecasts.

A quantile forecast is constructed as follows.
For $N$ given quantiles $\alpha_1,..., \alpha_N$, $q_1,..., q_N$ are the values
such that

\begin{equation}
  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., 
  P(Y \leq q_N) = \alpha_N
\end{equation}
When the quantiles are reported as prediction intervals we have more 
specifically

\begin{equation}
  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ...,
  P(Y \leq q_{N-1}) = 1 - \alpha_{N-1}, P(Y \leq q_N) = 1 - \alpha_N
\end{equation}

The quantile or interval format is somewhat unique among forecast 
representations discussed in this paper. What is possible for scoring forecasts
or building ensemble models in other representations is often not possible with
quantile forecasts. The shape of a distribution is also not known and in fact,
nothing is known about the tails of the uncertainty or ouside of the most 
extreme reported quantile values. In the Forecast Hub predictions, nothing 
is said about the range below the $1^{st}$ quantile or above the $99^{ths}$.
Yet the quantile representation has its advantages.

Quantile representation allows for forecasters to submit fairly detailed
forecasts without restricting the range of possible values.
Since quantiles are easily calculated from any regular distribution type
-e.g. quantile function for parametric functions or calculating sample 
quantiles- we consider quantile forecasts to have high flexbility in terms of 
what methods forecasters may employ in modeling.

To score predictions from a prediction interval, 
neither the LogS nor the CRPS may be used, 
but another proper scoring rule the interval score (IS) may be.
For an observed outcome $x^*$ and a prediction interval $(l,r)$ 
where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
the central $(1-\alpha)$ prediction interval the IS is defined as

\begin{equation}
\label{eq:is}
  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
  + \frac{2}{\alpha}(y-r)1\{x^* > r\}
\end{equation}
This is a sum -weighted by 
$\alpha$- of the width of the
interval and the distance between $x^*$ and the interval (if $x^*$ is not 
captured in the interval) \cite{gneiting2014probabilistic}. 
The IS requires only a single central 
$(1-\alpha) \times 100$ prediction interval.

When an interval forecast is made up of more than one interval with different
$\alpha$ levels, a weighted interval score (WIS) may be evaluated. Bracher et.
al use the WIS to evaluate COVID-19 inverval forecasts 
\cite{bracher2021evaluating}.
There are multiple versions of the WIS -some of 
which are described by Bracher et. al- but that used in the COVID-19 Forecast
Hub is defined as follows

\begin{equation}
  WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,y) \} )
\end{equation}
$w_k = \alpha_k/2$ is the weight on
intervals which was used. With that choice of weights, it may be shown that the
WIS approximates CRPS see S1 Text  \cite{bracher2021evaluating}

Like the CRPS, not only does the WIS provide an easily interpretable proper 
score for interval forecasts, but it may also be useful when building an 
ensemble forecast.

The ensemble forecast constructed by the COVID-19 Forecast Hub was made as an
equally-weighted average of forecasts from the component models. More 
specifically, each quantile value of the ensemble was the average of values from
all models corresponding to the same quantile \cite{ray2020ensemble}. For $M$ 
models each with $K$ quantiles, the $k^{th}$ ensemble quantile $q_k$ is 
calculated as

\begin{equation}
\label{eq:qa}
  q_k = \sum_{m=1}^M \nu_m q_k^m 
\end{equation}
where $\nu_m$ is the weight assigned to each forecast and $\sum \nu_m = 1$. In
the Forecast Hub model, $\nu_m = \nu = 1/M$. Where the overall mean or a
weighted mean may be used, the median may also be used.
Brooks et. al compare performance of the COVID-19 ensemble
between equally-weighted means, weighted means and median value constructions.
\cite{brooks2020comparing} (is is appropriate to cite this blog??)
In their report, they show that weighted means and median constructions tend
to outperform equally-weighted mean construction. To come up with optimal 
weights, they select values $\nu_m$ from \ref{eq:qa} which minimize the WIS of 
the ensemble forecast.

Averaging quantiles in this way the same as quantile averaging or Vincentization
only with an incomplete quantile function. It thus carries with it many of the
same characteristics.
Quantile averaging or Vincentization for a complete distribution is defined as

\begin{equation}
\label{eq:vinc}
  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
\end{equation}
where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
$0 < \alpha \leq 1$. Some notable characteristics are that it is more likely
to be unimodal than linear averaging of densities like BMA 
\cite{busetti2017quantile} (this paper is a comparison of QMA and 
linear or log averaging. Under some circumstances, such as when member
distributions are exponential, Weibull or logisitic the aggregated distribution
is the same \cite{ratcliff1979group}. It produces smoother
distributions than BMA according to Schepen and Wang \cite{schepen2015model}.
Lichtendahl et. al conclude that quantile averaging produces sharper forecasts
and tends to perform better in scoring than probability averaging
\cite{lichtendahl2013better}.

As in sample distributions and binned distributions, 
data storage for interval forecasts will
depend on the desired clarity of resolution. For the COVID-19 forecasts 
submitted to the forecast hub, twenty-three quantile values are requested for 
the quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This included a 
median along with eleven confidence intervals \cite{bracher2021evaluating}. This
requires forecasters to submit forty-six values in each short-term forecast 
(some of the longer term forecasts only include seven quantiles). In terms of 
storage, this is an improvement over requirements for the flu contest. Table
\ref{tab:qstor} shows what a submission of 23 quantiles from a 
Lognormal $(1,0.4)$ looks like.

% \begin{table}[h!]
% \centering
%  \begin{tabular}{|c|c|} 
%  \hline
%     quantile & value \\ \hline
%     0.01 & 1.07137 \\
%     0.025 & 1.2404 \\
%     0.05 & 1.40689 \\
%     0.01 & 1.62675 \\
%     ...  & ... \\
%     0.9 & 4.50667 \\
%     0.95 & 5.18328 \\
%     0.975 & 5.82391 \\
%     0.99 & 6.58783 \\
%  \hline
%  \end{tabular}
% \end{table}

\begin{table}[h!]
\centering
\label{tab:qstor}
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
 % \begin{tabular}{|c|c|}
 \hline
    quantile & 0.01 & 0.025 & 0.05  & ...  & 0.95 & 0.975 & 0.99 \\ \hline
    value & 1.07137 & 1.2404 & 1.40689 & ... & 5.18328 &
    5.82391 & 6.58783 \\
    % quantile & value \\ \hline
    % 0.01 & 1.07137 \\
    % 0.025 & 1.2404 \\
    % 0.05 & 1.40689 \\
    % 0.01 & 1.62675 \\
    % ...  & ... \\
    % 0.9 & 4.50667 \\
    % 0.95 & 5.18328 \\
    % 0.975 & 5.82391 \\
    % 0.99 & 6.58783 \\
 \hline
 \end{tabular}
\end{table}

@@

\subsection{Discrete mixture of parametric distributions}
In a parametric setting, forecasters may be permitted to submit a forecast as a
discrete mixture. Such a distribution may be constructed in the same way as the
ensemble described under Parametric distributions (\ref{eq:bma}) 
where for $T$ distributions
with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$

\begin{equation}
\label{eq:dmd}
  p^{M} = \sum_{t=1}^T z_tp_t(x)
\end{equation}

Like the standard parametric model, a discrete mixture is easily evaluated with
exisiting software (like distr R package \cite{camphausen2007distr}). And 
scoring may be done by 
using the LogS, CRPS and IS. The resolution of a discrete mixture is high 
and the support need not be limited by submission requirements.

An ensemble model may be built by using (\ref{eq:bma}) only replacing $p_m$
with $p^M$. Solving for weights may also be done similarly, though with the 
added complexity of component models being mixture distributions, the 
computation is likely to get more expensive. An example where this may be
especially true is when minimizing of CRPS, but the exact mixture doesn't 
result in CRPS in closed form \cite{baran2018combining}.

Depending on the number of components a forecaster includes in a mixture 
forecast, the amount of storage per forecast might be as little as for a 
parametric forecast and as much as a forecast hub will allow. For modelers whose
models produce distributions with irregular shapes, it may be that those
distributions can be closely approximated by the right mixture distribution.
